## Pizza Project Mid-Term {.tabset .tabset-fade}
**Authors: Sidney Schaeper & Morgan Miller **

### Introduction
### Packages Required
#### **Packages**
The packages that are need for this evaluation are the readr, dplyr, and ggplot2. The readr package helps us import the datasets for this project. You can find more information on the readr package by clicking [here](https://cran.r-project.org/web/packages/readr/readr.pdf). The dplyr package helps us clean the datasets. You can find more information on the dplyr package by clicking [here](https://www.rdocumentation.org/packages/dplyr/versions/0.7.8). The ggplot2 package helps us create visualizations for these datasets. You can find more information on the ggplot2 package by clicking [here](https://cran.r-project.org/web/packages/ggplot2/ggplot2.pdf). 

#### **Code to Install Packages**
```{r eval=FALSE}
install.packages("readr")
install.packages("dplyr")
install.packages("ggplot2")
```
#### **Code to Find Packages in the Library**
```{r results = "hide", warning = FALSE, message = FALSE}
library(readr)
library(dplyr)
library(ggplot2)
```
### Data Preparation
#### **Original Data Dictionary**

##### **Pizza Jared Variables**
Variable | Class | Description
---------|-------|------------
polla_qid | integer | quiz id
answer | character | answer (likert scale)
votes | integer | number of votes for that question/answer combo
pollq_id | integer | poll question id
question | character | pizza place
time | integer | time of quiz
total_votes | integer | total number of votes for that pizza place
percent | double | vote percent of total for that pizza place

##### **Pizza Barstool Variables**
Variable | Class | Description
---------|-------|------------
name | character | pizza place name
address1 | character | pizza place address
city | character | city
zip | double | zip
country | character | country
latitude | double | latitude
longitude | double | longitude 
price_level | double | price rating (the lower the number the cheaper the price)
provider_rating | double | provider review score
provider_review_count | double | provider review count 
review_stats_all_average_score | double | average score
review_stats_all_count | double | count of all reviews
review_stas_all_total_score | double | review total score

##### **Pizza Datafiniti Variables**
Variable | Class | Description
---------|-------|------------
name | character | pizza place
address | character | address
city | character | city 
country | character | country
province | character | state
latitude | double | latitude 
longitude | double |longitude
categories | character | restaurant category
price_range_min | double | price range min
price_range_max | double | price range max

#### **Setting the Working Directory and Reading the Datasets Into R**
The following is the code to read the datasets in the R. You first need to set the working directory to wherever the datasets are located. Next, you need to read the file into R. Before you set the working directory and the read datasets into R, you need to install the packages mentioned in the prior tab. Also, you need to find them in the library. The following code shows you how to do these steps. 

```{r eval = TRUE, results = "hide", fig.show = "hide", message = FALSE, warning = FALSE}
knitr::opts_knit$set(root.dir = getwd())
barstool <- read_csv("pizza_barstool.csv")
datafiniti <- read_csv("pizza_datafiniti.csv")
jared <- read_csv("pizza_jared.csv")
```
####Evaluate the Column Names and Values 
The first item we wanted to evaluate was the column names and the data types for each column in the barstool dataset. The first thing you should do is to make sure you have read in the dataset. Next, you should type in the following code into R. Finally, you should run the code. 
```{r}
head(barstool)
attributes(barstool)$spec
```
### Exploratory Data Analysis 