## Pizza Project Mid-Term {.tabset .tabset-fade}
**Authors: Sidney Schaeper & Morgan Miller **

### Introduction
### Packages Required
#### **Packages**
The packages that are need for this evaluation are the readr, dplyr, and ggplot2. The readr package helps us import the datasets for this project. You can find more information on the readr package by clicking [here](https://cran.r-project.org/web/packages/readr/readr.pdf). The dplyr package helps us clean the datasets. You can find more information on the dplyr package by clicking [here](https://www.rdocumentation.org/packages/dplyr/versions/0.7.8). The ggplot2 package helps us create visualizations for these datasets. You can find more information on the ggplot2 package by clicking [here](https://cran.r-project.org/web/packages/ggplot2/ggplot2.pdf). The first section of code allows you to install the packages. The second section of code allows you to load the packages into R. You need to run both of these sections of code in order to get these packages into R. 

##### **Code to Install Packages**
```{r eval=FALSE}
#Install packages necessary for this project#
install.packages("readr")
install.packages("dplyr")
install.packages("ggplot2")
```

##### **Code to Find Packages in the Library**
```{r results = "hide", warning = FALSE, message = FALSE}
#Load the installed packages into R#
library(readr)
library(dplyr)
library(ggplot2)
```

### Data Preparation
#### **Original Data Dictionary**

##### **Pizza Jared Variables**
Variable | Class | Description
---------|-------|------------
polla_qid | integer | quiz id
answer | character | answer (likert scale)
votes | integer | number of votes for that question/answer combo
pollq_id | integer | poll question id
question | character | pizza place
time | integer | time of quiz
total_votes | integer | total number of votes for that pizza place
percent | double | vote percent of total for that pizza place

##### **Pizza Barstool Variables**
Variable | Class | Description
---------|-------|------------
name | character | pizza place name
address1 | character | pizza place address
city | character | city
zip | double | zip
country | character | country
latitude | double | latitude
longitude | double | longitude 
price_level | double | price rating (0=cheap and 3=expensive)
provider_rating | double | provider review score
provider_review_count | double | provider review count 
review_stats_all_average_score | double | average score
review_stats_all_count | double | count of all reviews
review_stas_all_total_score | double | review total score
review_stats_community_average_score | double | community average score
review_stats_community_count | double | community review count
review_stats_community_total_score | double | community review total score
review_stats_critic_average_score | double | critic average score
review_stats_critic_count | double | critic review count
review_stats_critic_total_score | double | critic total score
review_stats_dave_average_score | double | Dave (Barstool) average score
review_stats_dave_count | double | Dave review count
review_stats_dave_total_score | double | Dave total score

##### **Pizza Datafiniti Variables**
Variable | Class | Description
---------|-------|------------
name | character | pizza place
address | character | address
city | character | city 
country | character | country
province | character | state
latitude | double | latitude 
longitude | double |longitude
categories | character | restaurant category
price_range_min | double | price range min
price_range_max | double | price range max

#### **Setting the Working Directory and Reading the Datasets Into R**
The following is the code to read the datasets in the R. You first need to set the working directory to wherever the datasets are located. Next, you need to read the file into R. Before you set the working directory and the read datasets into R, you need to install the packages mentioned in the prior tab. Also, you need to find them in the library. The following code shows you how to do these steps. 

```{r eval = TRUE, results = "hide", fig.show = "hide", message = FALSE, warning = FALSE}
#Set the working directory#
knitr::opts_knit$set(root.dir = getwd())

#Read the data sets into R#
barstool <- read_csv("pizza_barstool.csv")
datafiniti <- read_csv("pizza_datafiniti.csv")
jared <- read_csv("pizza_jared.csv")
```

####Evaluate the Column Names and Values 
The first item we wanted to evaluate was the column names and the data types for each column in the barstool dataset. The first thing you should do is to make sure you have read in the dataset. Next, you should type in the following code into R. Finally, you should run the code. The head code allows us to see a piece of the data. The names code allows us to see the name of the variables within the dataset. The attributes$spec code allows us to see the data types for each of the variables.

```{r}
#See a snippet of the barstool data set#
head(barstool)

#See the variable names of the barstool data set#
names(barstool)

#See the data types for the barstool variables#
attributes(barstool)$spec
```

After evaluating the outputs of the names and data types, there are multiple changes we believe that need to be changed. The first item we believe that needs to be changed is the name for address1. We decided to change the name for address1 to address, because it seemed more consistent with the other variable names. We believe the rest of the names of the variables are fine, and we don't need to change their names. You should the run the code below to change the name for address1.  

```{r}
#Change the name of address 1 to address for the barstool data set#
names(barstool)[2] <- "address"
```

The next items I wanted to change were the data types for zip, price_level, provider_review_count, review_stats_all_count, review_stats_community_count, review_stats_critic_count, and review_stats_dave_count. We decided to change zip from a double to a character, because we wanted to maintain the zeros in front of some of the zip codes. We decided to change price_level, provider_review_count, review_stats_all_count, review_stats_community_count, review_stats_critic_count, and review_stats_dave_count from a double to integer, because there should be no decimals with these numbers. Below is the code to change these data types. 

```{r}
#Change the data type of the items mentioned above#
barstool_data_type <- transform(barstool, zip = as.character(zip), price_level = as.integer(price_level), provider_review_count = as.integer(provider_review_count), review_stats_all_count = as.integer(review_stats_all_count), review_stats_community_count = as.integer(review_stats_community_count), review_stats_critic_count = as.integer(review_stats_critic_count), review_stats_dave_count = as.integer(review_stats_dave_count))

#Check that the data types were appropriately changed#
tibble(barstool_data_type)
```

### Exploratory Data Analysis 