## Pizza Project Mid-Term {.tabset .tabset-fade}
**Author: Sidney Schaeper and Morgan Miller **

### Introduction
### Packages Required
#### **Packages**
The packages that are need for this evaluation are the readr, dplyr, and ggplot2. The readr package helps us import the datasets for this project. You can find more information on the readr package by clicking [here](https://cran.r-project.org/web/packages/readr/readr.pdf). The dplyr package helps us clean the datasets. You can find more information on the dplyr package by clicking [here](https://www.rdocumentation.org/packages/dplyr/versions/0.7.8). The ggplot2 package helps us create visualizations for these datasets. You can find more information on the ggplot2 package by clicking [here](https://cran.r-project.org/web/packages/ggplot2/ggplot2.pdf). 

#### **Code to Install Packages**
```{r eval = FALSE}
install.packages("readr")
install.packages("dplyr")
install.packages("ggplot2")
```
#### **Code to Find Packages in the Library**
```{r eval = FALSE}
library(readr)
library(dplyr)
library(ggplot2)
```
### Data Preparation
#### **Original Data Dictionary**

###### **Pizza Jared Variables**
Variable | Class | Description
---------|-------|------------
polla_qid | integer | quiz id
answer | character | answer (likert scale)
votes | integer | number of votes for that question/answer combo
pollq_id | integer | poll question id
question | character | pizza place
time | integer | time of quiz
total_votes | integer | total number of votes for that pizza place
percent | double | vote percent of total for that pizza place

###### **Pizza Barstool Variables**
Variable | Class | Description
---------|-------|------------
polla_qid | integer | quiz id
answer | character | answer (likert scale)
votes | integer | number of votes for that question/answer combo
pollq_id | integer | poll question id
question | character | question
place | character | pizza place
time | integer | time of quiz
total_votes | integer | total number of votes for that pizza place
percent | double | vote percent of total for that pizza place

###### **Pizza Datafiniti Variables**
Variable | Class | Description
---------|-------|------------
name | character | pizza place
address | character | address
city | character | city 
country | character | country
province | character | state
latitude | double | latitude 
longitude | double |longitude
categories | character | restaurant category
price_range_min | double | price range min
price_range_max | double | price range max

### Exploratory Data Analysis 